Linear Ordered Attribute Grammar scheduling using SAT-solving

### 2014-10-18 paper/paper.tex
added a paragraph about the relation between nonterminal and production dependency graphs

>>>>

The nonterminal dependency graphs and production dependency graphs are consistent if 1) whenever there is a path from attribute $a$ to $b$ in a production dependency graph then there needs to be an edge from $a$ to $b$ in the nonterminal dependency graph in which $a$ and $b$ occur\footnote{There is no such nonterminal dependency graph if the two attributes belong to different nodes} and 2) if there is an edge from $a$ to $b$ in a nonterminal dependency graph then there needs to be an edge from $a$ to $b$ for all occurrences of $a$ and $b$ in the production dependency graphs.
